Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-06-25 size_differentiated_export.tex
Updates from Overleaf

Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics representing conditions in the northeast Pacific in the summertime. Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($\ll$1). \textit{Papa\_winter} aims at capturing wintertime ocean conditions in the region. A different dynamical regime is expected to dominate during wintertime when mixed layers are deeper and lateral density gradients enhanced, with sharper density fronts, filament-like features and localized Rossby number $\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km) \citep{Mensa_2013,Callies_2015,Thompson_2016}. The individual characteristics of each of \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.

@@

% \begin{table}
% \caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
% \centering
% \begin{tabular}{l c}
% \hline
%  Run  & Time (min)  \\
% \hline
%   $l1$  & 260   \\
%   $l2$  & 300   \\
%   $l3$  & 340   \\
%   $h1$  & 270   \\
%   $h2$  & 250   \\
%   $h3$  & 380   \\
%   $r1$  & 370   \\
%   $r2$  & 390   \\
% \hline
% \multicolumn{2}{l}{$^{a}$Footnote text here.}
% \end{tabular}
% \end{table}

@@

\begin{equation}
w_s (t) = w_s^0\exp(-\frac{2kt}{3})
\label{eq: sinking_velocity_remin}
\end{equation}
where $w_s^0$ is the initial sinking velocity at $t = 0$ days. In this study, the impact of remineralization is thus considered through the implementation of a time-dependent sinking velocity (Equation \ref{eq: sinking_velocity_remin}). While particles classes are classified based on their initial sinking-velocity, it is worth noting that over the length of the particle-tracking experiments that include remineralization (28 days), particle sinking speeds slow down to 10\% of their initial velocity, which correspond to 3.1\5.

@@

Two model experiments are designed to capture different dynamical conditions observed in the northeast Pacific Ocean in summer and winter. \textit{Papa\_summer} is initialized in early spring (doy 105) when the water column is characterized by a relatively deep mixed layer ($\sim$100 m) and a halocline located between 100 and 150 m (Figure \ref{fig: Papa_summer}). The forcing by a realistic, positive, net heat flux generates the restratification of the water column, with the development of a strong thermocline between 25 and 50~m leading to the shoaling of the mixed layer and a subsurface peak in $N^2$ at about 30 m (see Figure \ref{fig: Papa_summer}). A comparison between model outputs and monthly-averaged density profiles from underwater gliders collected in June and July over the period 2008-2009 yields correlation coefficients of $r = 0.87$ and $r = 0.88$, respectively. These high correlation suggest that \textit{Papa\_summer} numerical experiment captures the vertical spring and summer conditions in the northeast Pacific Ocean.

@@

%FIG6
\begin{figure}[ht!]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
	%\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right). Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain. For each sinking-velocity class, the net particle flux is shown by a thick line. Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
	\includegraphics[width = .8\linewidth]{figures/Fig6.png}
	\caption{[left] Gridded anomaly in the median depth of particles 25 days after particle release, in the Winter experiment. Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected based on a 1D gravitational model where $z = w_s\timest$. [right] Probability Distribution Function (PDF) of particles as a function of depth for each velocity class. The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions. Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies. Release depth is indicated by the thick dashed line.}	
	\label{fig: particle_depth_distribution}
\end{figure}

@@

%FIG7
\begin{figure}[t]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum}). Biomass export flux for the 5 m/day sinking-velocity class remains unchanged, as it is used as a reference class in Equation (\ref{eq: biomassjungeslope}) ($w_{s_0} = 5$ m/day).}
	\includegraphics[width = 1\linewidth]{figures/Fig7.png}
	\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom]. Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class. Both winter dynamics and steeper Junge slopes tend to increase the relative contribution of slower-sinking particles.}
	\label{fig: biomass_export}
\end{figure}

@@

 %In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa. Choosing the winter mixed layer as the export depth is most appropriate compared to other commonly chosen depth horizons (e.g., compensation depth, euphotic depth, etc.), as it reduces the chances of particles being re-entrained into the mixed layer the following winter \citep{Palevsky_2016,Palevsky_2018}. We first consider the case of conservative particles that do not remineralize in order to isolate the effects of ocean dynamics on export.

%The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier than slower-sinking particles. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of particle export flux closely follow the curves derived from considering gravitational sinking only (Figure \ref{fig: particle_export}a). The particle flux is therefore exclusively downward, as the sinking rate of the particles in these sinking-velocity classes are larger than the advective sinking velocity ($w_s > w_{flow}$; see Figure \ref{fig: dynamics}).

%\fixme{mention deviations from dashed line. Mention resuspension (less than 1\%) for slow-sinking particles only due to vertical velocities.}
%The percentage of simulated particles crossing the 100 m export horizon with time is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier and in larger proportions. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking only (Figure \ref{fig: particle_export}).

%Time series of particle fluxes in \textit{Papa\_winter} present major differences (Figure \ref{fig: particle_export}b). In every sinking-velocity class, particles reach the export horizon faster than expected from gravitational sinking. This hastened arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day. Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now exhibit a significant net downward flux within the first 15 days of the simulation. For example, over 20\% of particles sinking at 0.5 m/day is cumulatively exported within the first 28 days in \textit{Papa\_winter}, versus less than 5\% in \textit{Papa\_summer}. However, particle export is now stretched over longer periods of time due to particle resuspension. In fact, the upward flux of particles in \textit{Papa\_winter} tends to mirror the measured downward flux (Figure \ref{fig: particle_export}b), exhibiting similar features such as the sudden increase in particle flux occurring at day 68 due to a wind impulse generating internal waves (see Figure \ref{fig: Papa_winter}a). These similarities suggest that advecting processes leading to an export flux are mostly reversible (e.g., internal waves, cyclo-geostrophy due to meandering jet). However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring in the presence of submesoscale dynamics. %\fixme{do those irreversible pathways due to sinking out of the reversible pathway, or due to irreversible mechanisms?}

%The corresponding biomass export fluxes demonstrate that, in the presence of submesoscale dynamics, slow-sinking particles significantly contribute to the total export flux over timescales of days (Figure \ref{fig: biomass_export}b). The quasi steady-state reached in the biomass export flux of the three slowest sinking-velocity classes suggests that biomass export is driven by advective processes rather than gravitational sinking ($w_s<w_{flow}$). However, the 5 m/day particle class still exhibits a peak in the biomass export flux coinciding with the peak expected from a simple one-dimensional gravitational sinking model, suggesting that the export for this sinking-velocity class remains mostly gravitationally-driven.

%As anticipated from Figure \ref{fig: sinking_velocity_spectrum}, the Junge slope $\xi$ is a determining parameter that affects the contribution of slower-sinking classes in the presence of submesoscale dynamics. Figure \ref{fig: biomass_export} shows the biomass export fluxes in normalized units for two different Junge slopes. The contribution from slow-sinking particles to the total biomass export flux expectedly decreases with the Junge slope. The decrease in biomass export flux is constant through time and can be predicted using Equation (\ref{eq: biomassjungeslope}):

%\begin{equation}
%    \frac{B_{\xi_1}(w_s)}{B_{\xi_2}(w_s)} = \left(\frac{w_s}{w_{s_0}}\right)^{\frac{\xi_2-\xi_1}{2}}
    %\frac{Flux\times B_{\xi_1}}{Flux\times B_{\xi_2}} = \frac{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_1/2}}{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_2/2}} = \left(\frac{w_s}{w_s_0}\right)^{(\xi_2-\xi_1)/2}
%\end{equation}
%Using $\xi_1 = 2$ and $\xi_2 = 4$, as depicted in Figure \ref{fig: biomass_export}, the decrease in biomass export is 80\%, 90\%, and 99.5\% for the 1, 0.5 and 0.025 m/day particle classes, respectively. %\fixme{The evolution of the biological community through time that would affect the slope of the size spectrum also has direct consequences on the export of the slower-sinking particles.}

%The presence of submesoscale dynamics therefore both hastens particle export, and increases the number of exported slow-sinking particles, between a few percent and tens of percents, depending on the sinking-velocity class. This has large implications on the amount of biomass exported, as slower-sinking particles tend to be far more numerous than faster-sinking particles, despite containing less biomass per particle (i.e., $\xi >3$; see Figure \ref{fig: sinking_velocity_spectrum}). %While the particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).

% The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role of slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}). This is a logical result given the observed increase in the particle export flux when submesoscale features are present (Figure \ref{fig: particle_export}). The sinking class dominating export, however, is highly dependent on the Junge slope. As the Junge slope increases, the particle spectrum steepens, and the contribution of slower-sinking particles to the total exported biomass increases. For example, after 28 days, the 1 m/day particle class cumulatively exported 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively. However, slow-sinking particles are generally expected to remineralize on timescales shorter than their export timescale. The impacts of remineralization on export are considered in the following section.

@@

 Figure \ref{fig: biomass_export_remin} compares the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for $\xi = 4$ with and without the remineralization scheme. \fixme{As expected, the main impact of implementing particle remineralization is a decrease in the total amount of biomass through time} \fixme{refer to Fig 9?}.

  %FIG8
 \begin{figure}[t]
	\centering
	%\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi=4$. Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
	\includegraphics[width = 1\linewidth]{figures/Fig8.png}
	\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release. Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class. Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}	
	\label{fig: biomass_export_remin}
\end{figure}

 As previously detailed, downward fluxes of biomass are dominated by faster-sinking particles during summertime and in the absence of remineralization. This is due to the fact that the flux of biomass $\left<w_{tot}B\right> = \left<w_sB\right> + \left<wB\right>$ is driven by $\left<w_sB\right>$, despite a smaller relative biomass content per particle. This is characteristic of a gravitationally-driven system, where settling velocity dictates the contribution to downward fluxes. Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize. This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where PDFs of relative biomass per particle class are shifted towards weaker vertical velocities than in the absence of remineralization, as predicted by Equation \ref{eq: sinking_velocity_remin}. As a result, the gravitationally-driven term $\left<w_sB\right>$ decreases with time, and the downward flux of biomass becomes generally advectively-driven by day 25 (Figure \ref{fig: biomass_export_remin}). In a advectively-driven system where $\left<w_sB\right> < \left<w_B\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes. This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}c): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (60\%; see Figure \ref{fig: biomass_export_remin}a). When remineralization processes are considered, slower-sinking particles become the dominant contributor to biomass fluxes (see Figure \ref{fig: biomass_export_remin}c). As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics (82\%; see Figure \ref{fig: biomass_export_remin}b). Even after implementing our remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes (87\%; see Figure \ref{fig: biomass_export_remin}d).

@@

 %Including remineralization of particles significantly impacts the relative importance of sinking and advection to export for each particle class. In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles decelerate as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}). In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included. The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is implemented.

 %The biomass export flux is also reduced compared to the case with no remineralization. In a gravitationally-driven system such as during the summer in the northeast Pacific, captured in \textit{Papa\_summer}, the impact of remineralization on the amount of biomass exported grows as the sinking velocity decreases. In fact, in \textit{Papa\_summer} with no remineralization, several sinking-velocity classes contribute to the biomass export over different timescales (dash lines in Figure \ref{fig: biomass_export_remin}). Once remineralization is implemented, no particles in the slowest sinking class (0.5 m/day) reach the export horizon and the contribution of the 1 m/day class is reduced by several orders of magnitude.

 %In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities (Figure \ref{fig: particle_export}). The difference in the biomass export flux between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already being exported. As particles age, remineralization has an increasing impact and the difference in the biomass export flux increases at a rate controlled by the remineralization rate defined in (\ref{eq: remin_scheme}). An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the biomass export flux of the 0.025 m/day sinking-velocity class exceeds the biomass export flux from both the 0.5 and 1 m/day sinking-velocity classes. This result only occurs when a negative slope of the biomass spectrum is combined with remineralization.

@@

\subsection{Dynamical Regimes}
\label{sec: Discussion_model}
\textit{Papa\_summer} and \textit{Papa\_winter} experiments were designed to statistically capture the ocean dynamics at Station Papa (145$^o$W, 50$^o$N) in the northeast Pacific Ocean. After spin-up, the model demonstrated similar distribution of both horizontal ($M^2$) and vertical ($N^2$) density gradients to observations from underwater gliders (see Figures \ref{fig: Papa_summer}, \ref{fig: Papa_winter}, and \ref{fig: dynamics}). The two experiments, however, show significantly different distributions of $M^2$, with the winter distribution exhibiting a longer tail, suggesting sharper density gradients. The tail of the wintertime distribution is only partially captured by the glider data, due to the fact that underwater gliders sample gradients at a maximum resolution of about 10 km, while the model resolution is 500 m and therefore allows sharp submesoscale fronts and filaments to be captured in the distribution.

@@

Mixed layer ocean dynamics at station Papa change significantly between the winter and the summer. In the winter, submesoscale dynamics are intensified, and sharp fronts and filaments develop in the mixed layer. This seasonal change in dynamics is consistent with recent observations \citep{Thompson_2016, Buckingham_2016}, and models \citep{Brannigan_2015, Callies_2015, Rocha_2016}, characterizing the seasonal cycle of submesoscale dynamics. The winter intensification in submesoscale dynamics was proven to have an important impact on the downward flux of all sinking-velocity classes modeled in this experiment. \fixme{export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale; The former evidently needing to be shorter than the latter to efficiently export POC. Not sure I should talk about timescales anymore}

@@

In the absence of remineralization, both a steeper size spectrum slope ($\xi>3$ in this case) and enhanced submesocale dynamics increase the contribution of slower-sinking particle classes to the downward biomass flux. This is only when both of these conditions are combined, however, that slower-sinking particles dominate the downward flux of biomass (Figure \ref{fig: biomass_export}). This is a significant result, as Junge slopes greater than 3 have been observed in the ocean \citep{Kostadinov_2009, White_2015}. The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations describing the relationships between particle size, sinking velocity, and biomass content used in this study. Nevertheless, our results demonstrate that

%% This section answers the questions above in terms of total amount of biomass efficiently exported with and without remineralization 
In the absence of remineralization, the net effect of submesoscale dynamics on biomass export depends on the Junge slope coefficient (Figure \ref{fig: biomass_export}).

Over the course of our simulation, the biomass export flux is consistently enhanced when $\xi = 4$ in the presence of submesoscale dynamics. Therefore, export flux is only enhanced in the presence of submesoscale dynamics if the slope of the size spectrum is steep enough to compensate for the re-suspension of faster-sinking particles by upwards vertical currents at submesoscales. %Talk about the asymmetry in the vertical velocity PDF (see Figure \ref{fig: dynamics})? Showing stronger, more localized downwelling, and broader and weaker upwelling?

Introducing remineralization processes significantly decreases the biomass export flux. Counter-intuitively, however, remineralization processes further strengthen the impact of submesoscale dynamics on export. The difference between summertime and wintertime biomass fluxes is even larger when remineralization processes are included. This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to decelerate these particles and thus prolongs their export timescales. In the summer, almost the entirety of the sinking velocity spectrum is therefore affected as export is gravitationally-driven. In the winter, however, slower-sinking particles are exported through advective processes. Their export timescale is little affected by remineralization processes as it only depends on local ocean dynamics.

%% this part discusses the respective contributions of the different sinking-velocity classes
The contribution of a particle class to POC export generally increases with the sinking-velocity. That is, faster-sinking particles tend to dominate the export signal. However, this tendency can be reversed if the following condition is satisfied:

\begin{equation}
    N_{slow} > N_{fast} \times \left(\frac{w_{s_{fast}}}{w_{s_{slow}}}\right)^{\frac{3 - \xi}{2}}
    \label{eq: condition}
\end{equation}
where $N$ is the number of simulated particles exported, $w_s$ is the sinking velocity and $\xi$ is the Junge slope coefficient (see Equation (\ref{eq: powerlaw_radius})). The number of exported slower-sinking particles must therefore be large enough to compensate for the smaller biomass content than faster-sinking particles.

In a gravitationally-driven system (i.e., weak submesoscale activity), this can only be achieved by having  $N_{slow} \sim N_{fast}$ and $\xi>3$, as there are no mechanism capable of selectively exporting slower-sinking particles (i.e., $N_{slow} \leq N_{fast}$). Junge slopes greater than 3 are regularly observed in the ocean \citep{Kostadinov_2009, White_2015}. Our results suggest that, in these conditions, the export of biomass is dominated by an intermediate sinking-velocity class that sinks fast enough to be 100\% exported ($N_{slow} = N_{fast}$; see Figure \ref{fig: export_cartoon}a). Because of the negative slope in the biomass spectrum, the contribution to export of any particle class sinking at a faster rate will be smaller. The intermediate class responsible for the largest part of the export signal will vary with time and space as it depends on the parameter $\xi$, as well as on the export depth. As $\xi$ increases, the sinking-velocity of the dominant class decreases (see Equation (\ref{eq: condition})). A deeper export depth would have the opposite effect and increase sinking-velocity of the dominant class (Figure \ref{fig: export_cartoon}a). %Implementing remineralization processes only shifts the curve shown in Figure \ref{fig: export_cartoon}a towards faster-sinking classes: as particle remineralize, a larger portion of the sinking-velocity spectrum will not contribute to POC export, and a faster initial sinking-velocity is required for the export timescale to be shorter than the remineralization timescale.

%FIG9
 \begin{figure}[ht!]
	\centering
	\includegraphics[width = .65\linewidth]{figures/Fig9_cartoon_meso}\\[.2cm]
	\includegraphics[width = .65\linewidth]{figures/Fig9_cartoon_submeso}
	\caption{Schematics illustrating the respective contribution to export of particles with different sinking velocities for $\xi > 3$ in (a) a gravitationally-driven system (i.e., weak submesoscale dynamics), and (b) an advectively-driven system (i.e., strong submesoscale dynamics).}
	\label{fig: export_cartoon}
\end{figure}

In a system affected by submesoscale dynamics, localized strong downwelling vertical currents are generated. This effectively shortens the export timescale of slower-sinking particles, entering a regime where export timescales are shorter than remineralization timescales (Figure \ref{fig: export_cartoon}b). In this regime, slower-sinking particles significantly contribute to POC export, and can even dominate the export signal for large $\xi$. This scenario is captured in one of the Lagrangian experiment and shown in Figure \ref{fig: biomass_export}b, where the contribution to biomass export from the 0.025 m/day sinking class exceeds the one from the 0.5 m/day sinking class. This surprising result further emphasizes the key role played by slow-sinking particles in POC export, especially in the presence of submesoscale dynamics and large $\xi$.

>>>>

Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics representing conditions in the Northeast Pacific in the summertime. Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($\ll$1). \textit{Papa\_winter} aims at capturing wintertime ocean conditions in the region. A different dynamical regime is expected to dominate during wintertime when mixed layers are deeper and lateral density gradients enhanced, with sharper density fronts, filament-like features and localized Rossby number $\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km) \citep{Mensa_2013,Callies_2015,Thompson_2016}. The individual characteristics of each of \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.

@@

@@

\begin{equation}
w_s (t) = w_s^0\exp(-\frac{2kt}{3})
\label{eq: sinking_velocity_remin}
\end{equation}
where $w_s^0$ is the initial sinking velocity at $t = 0$ days. In this study, the impact of remineralization is thus considered through the implementation of a time-dependent sinking velocity (Equation \ref{eq: sinking_velocity_remin}). While particles classes are classified based on their initial sinking-velocity, it is worth noting that over the length of the particle-tracking experiments that include remineralization (28 days), particle sinking speeds slow down to 10\% of their initial velocity.

@@

Two model experiments are designed to capture different dynamical conditions observed in the Northeast Pacific Ocean in summer and winter. \textit{Papa\_summer} is initialized in early spring (doy 105) when the water column is characterized by a relatively deep mixed layer ($\sim$100 m) and a halocline located between 100 and 150 m (Figure \ref{fig: Papa_summer}). The forcing by a realistic, positive, net heat flux generates the restratification of the water column, with the development of a strong thermocline between 25 and 50~m leading to the shoaling of the mixed layer and a subsurface peak in $N^2$ at about 30 m (see Figure \ref{fig: Papa_summer}). A comparison between model outputs and monthly-averaged density profiles from underwater gliders collected in June and July over the period 2008-2009 yields correlation coefficients of $r = 0.87$ and $r = 0.88$, respectively. These high correlation suggest that \textit{Papa\_summer} numerical experiment captures the vertical spring and summer conditions in the Northeast Pacific Ocean.

@@

%FIG6
\begin{figure}[ht!]
	\centering
	\includegraphics[width = .8\linewidth]{figures/Fig6.png}
	\caption{[left] Gridded anomaly in the median depth of particles 25 days after particle release, in the Winter experiment. Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected based on a 1D gravitational model where $z = w_s\timest$. [right] Probability Distribution Function (PDF) of particles as a function of depth for each velocity class. The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions. Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies. Release depth is indicated by the thick dashed line.}	
	\label{fig: particle_depth_distribution}
\end{figure}

@@

%FIG7
\begin{figure}[t]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig7.png}
	\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom]. Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class. Both winter dynamics and steeper Junge slopes tend to increase the relative contribution of slower-sinking particles.}
	\label{fig: biomass_export}
\end{figure}

@@

@@

 Figure \ref{fig: biomass_export_remin} compares the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for $\xi = 4$ with and without the remineralization scheme. As previously detailed, downward fluxes of biomass are dominated by faster-sinking particles during summertime and in the absence of remineralization. This is due to the fact that the flux of biomass $\left<w_{tot}B\right> = \left<w_sB\right> + \left<wB\right>$ is driven by $\left<w_sB\right>$, despite a smaller relative biomass content per particle. This is characteristic of a gravitationally-driven system, where settling velocity dictates the contribution to downward fluxes. Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize. This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where PDFs of relative biomass per particle class are shifted towards weaker vertical velocities than in the absence of remineralization, as predicted by Equation \ref{eq: sinking_velocity_remin}. As a result, the gravitationally-driven term $\left<w_sB\right>$ decreases with time, and the downward flux of biomass becomes generally advectively-driven by day 25 (Figure \ref{fig: biomass_export_remin}). 
   %FIG8
 \begin{figure}[t!]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig8.png}
	\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release. Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class. Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}	
	\label{fig: biomass_export_remin}
\end{figure}
In a advectively-driven system where $\left<w_sB\right> < \left<w_B\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes. This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}c): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (60\%; see Figure \ref{fig: biomass_export_remin}a). When remineralization processes are considered, slower-sinking particles become the dominant contributor to biomass fluxes (see Figure \ref{fig: biomass_export_remin}c). As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics (82\%; see Figure \ref{fig: biomass_export_remin}b). Even after implementing our remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes (87\%; see Figure \ref{fig: biomass_export_remin}d).

@@

@@

\subsection{Dynamical Regimes}
\label{sec: Discussion_model}
\textit{Papa\_summer} and \textit{Papa\_winter} experiments were designed to statistically capture the ocean dynamics at Station Papa (145$^o$W, 50$^o$N) in the Northeast Pacific Ocean. After spin-up, the model demonstrated similar distribution of both horizontal ($M^2$) and vertical ($N^2$) density gradients to observations from underwater gliders (see Figures \ref{fig: Papa_summer}, \ref{fig: Papa_winter}, and \ref{fig: dynamics}). The two experiments, however, show significantly different distributions of $M^2$, with the winter distribution exhibiting a longer tail, suggesting sharper density gradients. The tail of the wintertime distribution is only partially captured by the glider data, due to the fact that underwater gliders sample gradients at a maximum resolution of about 10 km, while the model resolution is 500 m and therefore allows sharp submesoscale fronts and filaments to be captured in the distribution.

@@

Mixed layer ocean dynamics at station Papa change significantly between the winter and the summer. In the winter, submesoscale dynamics are intensified, and sharp fronts and filaments develop in the mixed layer. This seasonal change in dynamics is consistent with recent observations \citep{Thompson_2016, Buckingham_2016}, and models \citep{Brannigan_2015, Callies_2015, Rocha_2016}, characterizing the seasonal cycle of submesoscale dynamics. The winter intensification in submesoscale dynamics was proven to have an important impact on the downward flux of all sinking-velocity classes modeled in this experiment.

@@

In the absence of remineralization, both a steeper size spectrum slope ($\xi>3$ in this case) and enhanced submesoscale dynamics increase the contribution of slower-sinking particle classes to the downward biomass flux. This is only when both of these conditions are combined, however, that slower-sinking particles dominate the downward flux of biomass (Figure \ref{fig: biomass_export}). This is a significant result, as Junge slopes greater than 3 have been observed in the ocean \citep{Kostadinov_2009, White_2015}. The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations used in this study describing the relationships between particle size, sinking velocity, and biomass content. Nevertheless, our results demonstrate the importance of resolving the lower range of the particle spectrum when measuring vertical fluxes, especially when submesoscale dynamics are active. It also highlights the importance of better constraining the relationships linking particle size, sinking velocity, and biomass content.

Introducing remineralization processes significantly decreases the biomass flux. Counter-intuitively, however, the implementation of a remineralization scheme further strengthen the role played by slower-sinking particles in the biomass flux (Figure \ref{fig: biomass_export_remin}. This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as these particles decelerate as they remineralize. In the summer, all particle classes are similarly affected by the remineralization scheme as downward fluxes are gravitationally-driven. In the winter, however, slower-sinking particles are exported through advective processes. Their export timescale is little affected by remineralization processes as it only depends on local ocean dynamics.

The result of this study suggest that slow- and non-sinking particles must be considered when studying the downward flux of particulate matter in the upper ocean. The patchiness associated with both particle production and submesoscale features poses a real observational challenge to properly resolve vertical fluxes. Based on our findings, subsequent studies should focus on testing the impact of patchiness on vertical fluxes: In the wintertime, when size spectral slope is steep and submesoscale dynamics most active, vertical fluxes could be grossly underestimated depending on the level of co-occurrence between particle production and stronger vertical currents.

\section{Conclusion}
\label{sec: Conclusions}
The main conclusions of this study are: 
\begin{enumerate}
\item Ocean dynamics in the subpolar Northeast Pacific exhibit a seasonal cycle with low submesoscale activity in the summertime, and more submesoscale features present in the wintertime. Submesoscale dynamics generate larger, and asymmetrical, vertical currents leading to a vertical biomass flux driven by advective processes, as opposed to gravitationally-driven in the summertime.

\item Submesoscale dynamics generally enhance downward fluxes by increasing the contribution of slower-sinking particles to the total flux by increasing the number of particle advected downward by ocean currents. The contribution of slower-sinking particles to the total flux is found to be at least significant, and can be dominant in certain conditions.
\item Contribution of slower-sinking particles to downward biomass fluxes export depends on the slope of the particle size spectra (i.e., Junge Slope), that controls the relative number of particles per size class. Two cases emerge from this study:
\begin{enumerate}
	\item If the Junge slope is smaller than 3, larger particles contribute most to vertical biomass fluxes independently of flow dynamics, as there are no mechanism capable of selectively advecting slower-sinking particles. The system is described as gravitationally-driven.
	\item If the Junge slope is greater than 3, as most commonly observed, ocean dynamics become the determining factor on which particle classes dominate the downward fluxes: as submesoscale dynamics become more active, an ageostrophic circulation leading to larger vertical velocities develops. In these conditions, downward biomass fluxes are largely driven by the slower-sinking particle classes.
	\end{enumerate}
\item Remineralization processes logically reduce the amplitude of biomass fluxes. However, it unexpectedly enhances the role played by slower-sinking particles as the impact of remineralization is larger on faster-sinking particles by affecting both biomass content and sinking velocity.
\end{enumerate}
